Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
minor corrections

    The \texttt{send\_message()} call takes four additional parameters
    compared to the standard Berkeley Sockets API. These are 1) a message
    sequence number, that can be used to re-order messages and detect
    message loss; 2) a relative deadline, which is combined with an
    estimate of the current round-trip-time, and the time that the message
    has spent in the sending buffer, to determine if a message will arrive
    in time to be played-out; 3) the sequence number of any message on
    which this depends, for example the sequence number of a video I-frame
    on which a P-frame is predicted; and 4) a sub-stream identifier, used,
    for example, to differentiate audio, video, sub-title, control, and
    repair streams.

@@

A message that won't arrive within its lifetime is considered to have
\emph{expired}. Applications specify the application-level sequence number
of a message they depend on (\texttt{depends\_on}). If the message depends
on a message that has expired, then it too is considered to have expired.
The partial reliability service follows from the deadline and dependency
services: messages will be reliably transmitted until they expire.

>>>>

    The \texttt{send\_message()} call takes four additional parameters
    compared to the standard Berkeley Sockets API. These are 1) a
    message sequence number, that can be used to re-order messages and
    detect message loss; 2) a relative deadline, which is combined
    with an estimate of the current round-trip-time, and the time that
    the message has spent in the sending buffer, to determine if a
    message will arrive in time to be played-out; 3) the message
    sequence number of any message on which this depends, for example,
    of a video I-frame on which a P-frame is predicted; and 4) a
    sub-stream identifier, used, for example, to differentiate audio,
    video, sub-title, control, and repair streams.

@@

A message that won't arrive within its lifetime is considered to have
\emph{expired}. A message is also considered to have expired if its
message sequence number dependency, \texttt{depends\_on},
%on which a message depends, . If the message depends on a message that has expired, then it too is considered to have
has expired. A partial reliability service follows
from this deadline and dependency service: messages will be reliably
transmitted until they expire.
